Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-29 ms.tex
getting rid of incorrect statements in model prediction discussion

This equation is quite similar to Equation \ref{equ:iras}, but with two 
important differences. First, the normalization of $\tilde{I}_{\nu_i}$ is now 
specified by $\tilde{I}_{545}$, which represents the flux density per solid
angle measured in the \PLANCK~545 GHz band. The denominator serves to ensure 
that, for the case of $\nu_i$=545 GHz, $\tilde{I}_{545}$ is self-consistent. 
Second, each term in the numerator is multiplied by a conversion factor 
$u_{\nu_i}^{-1}(T_k, \beta_k)$. This factor is necessary because some of the 
\PLANCK~maps of interest have units of $K_{CMB}$ (100-353 GHz), while the
remaining maps (545-3000 GHz) have units of MJy/sr. Complicating matters, the 
conversion from $K_{CMB}$ to MJy/sr depends on the spectrum under 
consideration; attempting to apply conversion factors to put all of the 
observed maps themselves into common units is not a particularly attractive 
option. Therefore, we adopt the strategy of predicting each band in its native 
units, whether MJy/sr or $K_{CMB}$. For this reason, we always evaluate 
$B_{\nu_{i,c}}$ in Equation \ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 
(dimensionless) for all $\nu_i$$\ge$545 GHz. For $\nu_i$$\le$353 GHz, 
$u_{\nu_i}(T_k, \beta_k)$ represents the appropriate conversion factor from 
$K_{CMB}$ to MJy/sr:

% equation for u goes here

\begin{equation}
u_{\nu_i}(T, \beta) = u_{\nu_i, IRAS} \times u_{\nu_i, IRAS \ to \ (T, \beta)}
\end{equation}

Here $u_{\nu_i, IRAS}$ gives the conversion factor from $K_{CMB}$ to MJy/sr
for band $\nu_i$ under the `\IRAS~convention', which corresponds to
a power law specrum with spectral index $\alpha$=$-1$. The values of 
$u_{\nu_i, IRAS}$ are listed in the second column of \cite{planckresponse} 
Table 6. $u_{\nu_i, IRAS \ to \ (T, \beta)}$ is a color correction factor 
relative to the \IRAS~convention for band $\nu_i$, assuming a MBB($T$, $\beta$)
spectrum. In practice, we retrieve $u_{\nu_i}(T, \beta)$ values in a fashion 
similar to that used for the $b_{\nu_i}(T, \beta)$ color corrections, using a 
set of precomputed one-dimensional look-up tables. To reiterate, for 
$\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ has units of (MJy/sr)/$K_{CMB}$,
and therefore $\tilde{I}_{\nu_{i}}$ will have different units depending on the 
band $\nu_i$, though $\tilde{I}_{\nu_{i}}$ always has the same units as the 
native band $\nu_i$ map.

%We will treat the SED normalization $\tilde{I}_{545}$ as a free 
%parameter in our fitting procedure. In our baseline fits, second free 
%parameter is $T_2$, which determines the shape of the SED through $M_{\nu}$ as
% well as $b_{\nu_i}(T_2)$.

% introduce nu_i notation in above paragraph with some mention of what it
% means

>>>>

This equation is quite similar to Equation \ref{equ:iras}, but with two 
important differences. First, the normalization of $\tilde{I}_{\nu_i}$ is now 
specified by $\tilde{I}_{545}$, which represents the flux density per solid
angle measured in the \PLANCK~545 GHz band. The denominator serves to ensure 
that, for the case of $\nu_i$=545 GHz, $\tilde{I}_{545}$ is self-consistent. 
Second, each term in the numerator is multiplied by a conversion factor 
$u_{\nu_i}^{-1}(T_k, \beta_k)$. This factor is necessary because some of the 
\PLANCK~maps of interest have units of $K_{CMB}$ (100-353 GHz), while the
remaining maps (545-3000 GHz) have units of MJy/sr. We have adopted the 
strategy of predicting each band in its native units, whether MJy/sr or 
$K_{CMB}$. For this reason, we always evaluate $B_{\nu_{i,c}}$ in Equation 
\ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 (dimensionless) for all 
$\nu_i$$\ge$545 GHz. For $\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ 
represents the conversion factor from $K_{CMB}$ to MJy/sr, given by 
\cite{planckresponse} Equation 32.

%is the old sentence below worth reinstating ?

%To reiterate, for 
%$\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ has units of 
%(MJy/sr)/$K_{CMB}$,and therefore $\tilde{I}_{\nu_{i}}$ will have different 
%units depending on the band $\nu_i$, though $\tilde{I}_{\nu_{i}}$ always has 
%the same units as the native band $\nu_i$ map.
